\documentclass{article}
\usepackage{geometry}
\usepackage[]{hyperref}
\usepackage{titlesec}
\titleformat{\section}
  {\Large\bfseries}  % Format
  {}{0em}           % Label
  {}                % Separator
  [\vspace{-0.5em}] % After-code

\geometry{
    a4paper,
    total={170mm,257mm},
    left=20mm,
    top=20mm,
}

\begin{document}

\vspace*{-40pt}  % Reduces space at top of page
\begin{center}
    \huge\textbf{Algon}\\[3pt]  % [3pt] adds a bit of controlled spacing
    \small Algon33.ar@gmail.com
\end{center}
\vspace{10pt}  % Add some space before first section


\textbf{MPhys. Physics with Theoretical Physics}, University of Manchester\\
Thesis: ``The Polaron Transform Applied to a Landau-Zener Transition'' 

\section*{Experience/Projects}
\vspace{10pt}  % Add some space before first section
\textbf{AI Evaluation Specialist}, Equistamp.com
\begin{itemize}
    \item Finding and augmenting high-quality AI capability evaluations
\end{itemize}

\textbf{Stampy/AIsafety.info Distillation Fellow and Project Lead}
\begin{itemize}
    \item Initially, I wrote intro materials for AI safety, and then shifted to leading the Stampy project. 
    \item Examples of articles I have helped to write include \href{https://aisafety.info/questions/8OGF/What-is-the-"natural-abstraction-hypothesis"}{What is the "natural abstraction hypothesis"?}  and \href{https://aisafety.info/questions/8EL9/What-is-AI-alignment}{What is AI alignment?}
    \item As project lead, I've had to change stampy's culture to prioritize one thing at a time, and focus on creating content that address people's needs. This meant doing things like: creating a new intro section designed for laymen, positioning the site better, trying out new mediums etc. 

\end{itemize}

\textbf{Short term contracts}
\begin{itemize}
    \item ``Ambitious Methods in Education''. A report for the Atlas Fellowship on methods in education greatly surpassing those in common use along one of four axis: generality, effectiveness, cost and scalability.   
    \item ``Detecting Strategic Reasoning in AI Systems''. A report on ways to determine to what extent near-term AI systems possess the bundle of skills Bostrom calls the "Strategic superpower".   
    \item Automated Metaculus Predictions: A bot I wrote for a superforecaster who wanted easy Metaculus points winnable by simply copying the aggregate community probability distributions on all questions on Metaculus.  
\end{itemize}


\end{document}